The evolution of gene expression in the term placenta of viviparous mammals

### 2015-11-03 manuscript/manuscript.Rnw
add a species tree

>>>>

\begin{figure}
<<species.tree,fig.width=8,fig.height=6,echo=FALSE>>=
species.tree <- 
    read.tree(text="(Monodelphis_domestica,((Dasypus_novemcinctus,Loxodona_africana),((Canis_familiaris,(Equus_caballus,(Sus_scrofa,(Ovis_aries,Bos_taurus)))),(((Spalax_carmeli,Nannospalax_galili),Mus_Musculus),((Pan_paniscus,Homo_sapiens),Ateles_fuciceps)))));")
plot(species.tree,x.lim=18)
edgelabels("Eutheria",2,frame="none",bg="white",font=1,adj=c(0.75,0),cex=0.9)
edgelabels("Euarchontoglires",16,frame="none",bg="white",font=1,adj=c(0.5,0),cex=0.9)
edgelabels("Laurasiatheria",7,frame="none",bg="white",font=1,adj=c(0.5,0),cex=0.9)
edgelabels("Atlantogenata",3,frame="none",bg="white",font=1,adj=c(0.5,0),cex=0.9)
edgelabels("Boreoeutheria",6,frame="none",bg="white",font=1,adj=c(0.7,0),cex=0.9)
@ 
\caption{Species tree for organisms studied}
\label{fig:species_tree}
\end{figure}
